markov_chains

### 2017-03-21 San Antonio/markov_chains.Rmd
Update markov_chains.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(plyr)
require(RcppRoll)
require(markovchain)
require(reshape)
```
```{r setting directories}
knitr::opts_knit$set(root.dir = "~/Documents/Violation_Project")
setwd("~/Documents/Violation_Project")

@@

temp$cluster <- clustering$cluster
temp$date <- paste(as.character(temp$year), "-" , as.character(temp$quarter))
temp2 <- temp %>% select(mine_id, cluster, date)
melted <- melt(temp2, id=c("mine_id", "date"))
aggregate_cluster_seq <- cast(melted, mine_id~date)
```

Markov Chain function
```{r}
markov <- function(x){
  x <- as.integer(x)
  cluster_seq_raw <- x[!is.na(x)]
  if(length(cluster_seq_raw) > 1){
    cluster_sequence <- cluster_seq_raw[2:length(cluster_seq_raw)]
    cur_markov_chain <- markovchainFit(data=cluster_sequence)
    return (list("mine_id" = x[1], "markov_chain" = cur_markov_chain$estimate@transitionMatrix, "num_rows" = length(cluster_seq_raw)))
  }
  return (list("mine_id" = x[1], "markov_chain" = NA, "num_rows" = 0))
}
```

@@

```{r}
num_rows_ind <- sapply(result, "[[", 3)
weights <- num_rows_ind/sum(num_rows_ind)

markov_chains_ind <- sapply(result, "[[", 2)

weighted_transition <- mapply(function(x,y) x * y, x = weights, y = markov_chains_ind)

@@

for(i in 1:length(weighted_transition)){
  final_transition <- add_matrices_1(final_transition,weighted_transition[[i]])
}
final_transition

>>>>

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(plyr)
require(RcppRoll)
require(markovchain)
require(reshape)

```{r}
knitr::opts_knit$set(root.dir = "~/Documents/Violation_Project")
setwd("~/Documents/Violation_Project")

@@

temp$cluster <- clustering$cluster
temp$date <- paste(as.character(temp$year), "-" , as.character(temp$quarter))
temp2 <- temp %>% select(mine_id, cluster, date)
melted <- melt(temp2, id=c("mine_id", "date"))
aggregate_cluster_seq <- cast(melted, mine_id~date)

aggregate_cluster_seq
```

Markov Chain function
```{r}
markov <- function(x){
  x <- as.integer(x)
  cluster_seq_raw <- x[!is.na(x)]
  if(length(cluster_seq_raw) > 1){
    cluster_sequence <- cluster_seq_raw[2:length(cluster_seq_raw)]
    cur_markov_chain <- createSequenceMatrix(cluster_sequence, sanitize = FALSE)
    return (list("mine_id" = x[1], 
                 "markov_chain" = cur_markov_chain, 
                 "num_rows" = length(cluster_seq_raw),
                 "low" = 2 %in% cluster_sequence, "mid" = 1 %in% cluster_sequence, "high" = 3 %in% cluster_sequence
                 )
            )
  }
  return (list("mine_id" = x[1], 
               "markov_chain" = NA, 
               "num_rows" = 0,
               "low" = FALSE, "mid" = FALSE, "high" = FALSE
               )
          )
}

@@

```{r}
#transition matrix
markov_chains_ind <- sapply(result, "[[", 2)

@@

for(i in 1:length(weighted_transition)){
  final_transition <- add_matrices_1(final_transition,markov_chains_ind[[i]])
}
print("Tranition matrix frequency")
final_transition

final_markov<- matrix(rep(0,times= 9), ncol = 3, nrow = 3)
for(i in 1:3){
  final_markov[i,] <- final_transition[i,]/sum(final_transition[i,])  
}

print("Transition matrix probability")
final_markov
